---
format: 
  revealjs:
    navigation-mode: vertical
    slide-number: false
    width: 1600
    height: 900
    logo: "images/albert.jpg"
    footer: "[home page](https://mchiapello.github.io/2023_Einstein_MB/)"
    css: ["css/theme.css", "css/custom.css"]
    theme: simple
    controls: true
editor: source
filters:
  - roughnotation
editor_options: 
  chunk_output_type: inline
---

##  {#TitleSlide data-menu-title="TitleSlide" background-image="images/back001.jpg" background-size="cover" background-opacity="0.3"}

```{r setup, include=FALSE}
library(fontawesome)
library(tidyverse)
library(quarto)
library(gt)
library(gtExtras)
library(gtsummary)
```

<style>
  @import url('https://fonts.googleapis.com/css2?family=Architects+Daughter&family=Julius+Sans+One&family=Montserrat:wght@300&family=Rock+Salt&display=swap');
</style>

::: {style="position: absolute; left: 180px; top: 200px; height: 400px; width: 1500px; background-color: #69b1e9; padding: 20px; padding-left: 50px; border-radius: 5px;"}
[Course Introduction]{style="font-size: 120px; font-weight: bold; line-height: 1em; margin: 0px; font-family: 'Architects Daughter', cursive;"}

<br> <br>

[Marco Chiapello, PhD]{style="font-size: 40px; font-weight: bold;"}

[2023-12-15]{style="font-size: 30px;font-weight: bold;"}
:::

#  {background-image="images/back002.jpg" background-size="cover" background-opacity="0.3"}

[Introduce ourself]{.tit .p-span-center}

[{{< fa id-card >}}]{.icon .p-span-center}

:::{.notes}
- Introduce myself (long version)

- Give 10 minutes to write down a short presentation of themself
:::

##  {background-image="images/website.png" background-size="cover" background-opacity="0.1"}

[Website]{.p-span-center style="font-size: 100px"}

```{r}
#| echo: false
#| layout-ncol: 1
plot(qrcode::qr_code("https://mchiapello.github.io/2023_Einstein_MB/"))
```


:::{.notes}
Explain all the details on the website
:::


